%% ------------------------------------------------------------------------
%% Copyright 2012 Eric Fritz (eric@eric-fritz.com).
%% Modified by Kevin Wiskia (kevin@wiskia.com).
%% ------------------------------------------------------------------------

\documentclass[]{clean-resume}

%% ------------------------------------------------------------------------
%% Resume
%% ------------------------------------------------------------------------

\begin{document}

\header{Kevin}{Wiskia}{Software Engineer}

%%
%% Reset list margins, has to be done after header
\setlist[itemize]{leftmargin=*}

%%
%% Contact

\begin{aside}
  \section{Contact}
    433 W. Johnson St. \#1100
	Madison, WI 53703
    ~
    (608) 359-6972
    \href{mailto:dakman@gmail.com?subject=Resume}{dakman@gmail.com}
\end{aside}

%%
%% Skills

\section{Skills}

\begin{centering}
{ \small
	C\# $\cdot$
	Java $\cdot$
	PHP $\cdot$
	Python $\cdot$
	Ruby $\cdot$
	TypeScript $\cdot$
	JavaScript $\cdot$
	jQuery $\cdot$
	Backbone $\cdot$
	Marionette $\cdot$
	React $\cdot$
	Redux $\cdot$
	Angular $\cdot$
	Single Page Applications $\cdot$
	Webpack $\cdot$
	Node.JS $\cdot$
	SQL Server $\cdot$
	NoSQL paradigms $\cdot$
	Redis $\cdot$
	Elastic Search $\cdot$
	Varnish Cache $\cdot$
	HTML $\cdot$
	CSS $\cdot$
	Drupal $\cdot$
	WebSphere Portal $\cdot$
	IBM i $\cdot$
	Ubuntu Server $\cdot$
	CentOS $\cdot$
	Windows Server $\cdot$
	PowerShell $\cdot$
	Bash $\cdot$
	Git $\cdot$
	GitFlow $\cdot$
	Team City $\cdot$
	Jenkins $\cdot$
	Octopus Deploy $\cdot$
	Visual Studio $\cdot$
	Spring Framework $\cdot$
	.NET Core \& Framework $\cdot$
	Entity Framework $\cdot$
	WPF $\cdot$
	WCF $\cdot$
	UX Design $\cdot$
	Photoshop $\cdot$
	GIMP $\cdot$
	Inkscape $\cdot$
	Mobile First Design $\cdot$
	Responsive Web Design $\cdot$
	RESTful Web Services $\cdot$
	Horizontal Scalability $\cdot$
	Cloud \& Serverless Infrastructure $\cdot$
	Docker $\cdot$
	SignalR $\cdot$
	Microservices $\cdot$
	Payment Systems $\cdot$
	Video Platforms $\cdot$
	Logistics Systems
}
\end{centering}

\section{Career History}

\entry
	{Lead Software Engineer}
	{Full Stack, Design, Leadership}
	{Sonic Foundry - Madison, WI}
	{2016 - 2019}
	{
		\begin{itemize}
			\item Working on an enterprise video platform responsible for capturing, transcoding, and delivery of video content. With a focus on playback functionality and engagement.

			\item Development of new features, and greenfield products from the ground up. Everything from conceptualation, design, production, and delivery. These products helped meet a market demand, and increased sales.

			\item Headed efforts to modernize both front and back end code infrastructures.

			\item Oversaw a team of developers and managed development of projects.

			\item Kept team up to date on new trends in software development, and how we could leverage them.
		\end{itemize}
		\tech{C\#, .NET Entity Franekwork/MVC, SPA, JavaScript, Bootstrap, Backbone, Marionette}
	}

\entry
	{Software Engineer}
	{Full Stack, Design}
	{ABC Supply Co. - Beloit, WI}
	{2010 - 2016}
	{
		\begin{itemize}
			\item Saved thousands of man-hours daily through automated route planning for delivery trucks, and ensuring that those routes conform to the DOT's hours of service regulations.
		
			\item Increased conversion rate on ecommerce platform by streamlining checkout process while adhering to PCI compliance.
			
			\item Reduced human error, and saved time by creating a system to determine a salesperson's commissions from sales data and submits payment to a payroll system (ADP).
		
			\item Improved team productivity by implementing smarter branching in git, unit tests, continuous integration, and automated deployments.
		
			\item Unified look and feel and user experience between platforms by establishing and executing a style guide.
		
			\item Kept coworkers up to date by teaching new technology, and preparing sessions on topics such as optimizing web pages, and taking advantage of toolsets.
		\end{itemize}
		
		\tech{Java, C\#, PHP, Python, Ruby, SQL, HTML, JavaScript, CSS, SASS, UX Design, SOA, MVC}
	}

\entry
	{Software Engineer}
	{Full Stack, Design}
	{Foremost Media - Janesville, WI}
	{2010}
	{
		\begin{itemize}
			\item Helped clients stay connected and organized with their customers by creating a lead management system that organized customer interactions and capture leads through embedable website widgets.

			\item Worked with clients directly to design applications tailored to their needs.
		\end{itemize}
		
		\tech{C\#, PHP, SQL, JavaScript, HTML, CSS}
	}

\newpage

\entry
	{Software Engineer}
	{Full Stack, Design}
	{ESDN, Inc. - Janesville, WI}
	{2008 - 2009}
	{
		\begin{itemize}
			\item Created a program that would take manufacturer product specifications and create "certificates" which would be rendered to an image and automatically printed on plastic cards.

			\item Increased curb-appeal by creating a visually-appealing kiosk application to display products in inventory.

			\item Created a web application that would manage an incentive program that would direct deposit money into a salesperson's account.
		\end{itemize}
		
		\tech{C\#, SQL, JavaScript, HTML, CSS, XAML, WCF}
	}

\end{document}
